Differentiation By Year

### 2017-08-25 doc/RMD/by-year.Rmd
update colors on by-year

```{r dapc, cache = TRUE}
setPop(dat11cc) <- ~Region/Year
set.seed(2017-08-18)
regyear.dapc <- xvalDapc(tab(dat11cc), pop(dat11cc), n.pca.max = 20, n.rep = 1000)$DAPC
regyear.dapc
```

@@

gg_region_year <- ggscatter(regyear.dapc, strata(dat11cc)) +
  facet_wrap(~Region) +
  theme(legend.position = c(0.75, 0.1)) +
  guides(color = guide_legend(nrow = 4)) +
  theme(legend.direction = "horizontal") +
  theme(strip.background = element_rect(color = NA, fill = "grey90")) +
  theme(strip.text = element_text(face = "bold", hjust = 0.05)) +
  theme(panel.border = element_blank())
gg_region_year
if (!interactive()) {
  ggsave(filename = file.path(PROJHOME, "results/figures/publication/dapc_region_year.pdf"),
         plot = gg_region_year,
         width = 7,
         height = 7)
}

@@

```{r dapc_plot_newamica, fig.width = 5, fig.height = 4, warning = FALSE, message = FALSE}
gg_region_year_micanewa <- ggscatter(regyear.dapc, strata(dat11cc), filter = quo(Region %in% c("WA", "CA", "NE", "MI"))) +
  facet_wrap(~Region, nrow = 2) +
  theme(legend.position = "right") +
  theme(legend.justification = "bottom") +
  theme(legend.box.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(legend.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(strip.background = element_rect(color = NA, fill = "grey90")) +
  theme(strip.text = element_text(face = "bold", hjust = 0.05)) +
  theme(panel.border = element_blank()) +
  theme(legend.key = element_rect(fill = "grey95"))
gg_region_year_micanewa
if (!interactive()) {
    ggsave(filename = file.path(PROJHOME, "results/figures/publication/dapc_region_year_micanewa.pdf"),
       plot = gg_region_year_micanewa,
       width = 88,
       height = 0.8*88,
       units = "mm",
       scale = 1.25
       )
}
```

@@

```{r NEplot, fig.width = 12, fig.height = 14}
gglNE <- suppressMessages(ggloc(loc, "NE", 2003:2012))
cowplot::plot_grid(plotlist = gglNE, labels = names(gglNE), ncol = 2)
```
```{r MIplot, fig.width = 10, fig.height = 12}
gglMI <- suppressMessages(ggloc(loc, "MI", 2003:2012))
cowplot::plot_grid(plotlist = gglMI, labels = names(gglMI), ncol = 2)
```

>>>>

```{r dapc, cache = TRUE}
setPop(dat11cc) <- ~Region/Year
set.seed(2017-08-18)
regyear.dapc <- xvalDapc(tab(dat11cc), pop(dat11cc), n.pca = 4:20, n.rep = 1000)$DAPC
regyear.dapc
```

@@

yearscale <- viridis::viridis(nlevels(strata(dat11cc)$Year), option = "C")
names(yearscale) <- sort(levels(strata(dat11cc)$Year))
gg_region_year <- ggscatter(regyear.dapc, strata(dat11cc)) +
  facet_wrap(~Region) +
  theme(legend.position = c(0.75, 0.1)) +
  guides(color = guide_legend(nrow = 4)) +
  scale_color_manual(values =  yearscale, breaks = names(yearscale)) +
  theme(legend.direction = "horizontal") +
  theme(strip.background = element_rect(color = NA, fill = "grey90")) +
  theme(strip.text = element_text(face = "bold", hjust = 0.05)) +
  theme(panel.border = element_blank())
gg_region_year
if (!interactive()) {
  ggsave(filename = file.path(PROJHOME, "results/figures/publication/dapc_region_year.pdf"),
         plot = gg_region_year,
         width = 7,
         height = 7)
}

@@

```{r dapc_plot_newamica, fig.width = 5, fig.height = 4, warning = FALSE, message = FALSE}
gg_region_year_micanewa <- ggscatter(regyear.dapc, strata(dat11cc), filter = quo(Region %in% c("WA", "CA", "NE", "MI"))) +
  facet_wrap(~Region, nrow = 2) +
  theme(legend.position = "right") +
  theme(legend.justification = "bottom") +
  scale_color_manual(values =  yearscale, breaks = names(yearscale)) +
  theme(legend.box.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(legend.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(strip.background = element_rect(color = NA, fill = "grey90")) +
  theme(strip.text = element_text(face = "bold", hjust = 0.05)) +
  theme(panel.border = element_blank()) +
  theme(legend.key = element_rect(fill = "grey95"))
gg_region_year_micanewa
if (!interactive()) {
    ggsave(filename = file.path(PROJHOME, "results/figures/publication/dapc_region_year_micanewa.pdf"),
       plot = gg_region_year_micanewa,
       width = 88,
       height = 0.8*88,
       units = "mm",
       scale = 1.25
       )
}
```

@@

```{r NEplot, fig.width = 12, fig.height = 14}
gglNE <- suppressMessages(ggloc(loc, "NE", 2003:2012))
cowplot::plot_grid(plotlist = gglNE, labels = names(gglNE), ncol = 2)
```
```{r MIplot, fig.width = 12, fig.height = 14}
gglMI <- suppressMessages(ggloc(loc, "MI", 2003:2012))
cowplot::plot_grid(plotlist = gglMI, labels = names(gglMI), ncol = 2)
```
